\section* {Motivation letter}

I hereby apply for the position 24/2017, Open Science Blog Editor.



I used to work in fundamental research (neuro-genetics, my second post doc - 2009 to 2014- was under Bjoern Brembs supervision), and got more interested in project management and pragmatic ways to improve scientific outputs in the recent years. I have been running the blog for Drososhare GmbH since 2014, and I am using twitter intensively in relation to my work there (@drososhare), and for my open science projects (@j\_colomb). I am for instance involved in the production of a MOOC for open science. I have a strong commitment to open data and other aspects of reproducible research standards (open access, reproducible reports, pre-registrationg). Please have a look at the links for more information.


Working for the OSL would be a great pleasure and opportunity, I could finally focus my attention and work on pushing open science forward (especially in Germany and in Europe), and get the means to have a real impact. I am in close contact with Dr Jon Tennant and we would like to discuss whether the position might be split, maybe between the two of us since our skills are complementary.

I am looking forward to hear from you,

Dr. Julien Colomb

\vspace {1cm} 

Links:

My website on teaching open science: \\ \url{https://reproducibleresearch.wordpress.com/}

The video pitch for my open science workshop:   \\ \url{https://vimeo.com/216695191}

The open science meetup I am co-organising: \\ \url{http://www.meetup.com/Berlin-Open-Science-Meetup/}

The Drososhare blog: \\ \url{https://drososhare.wordpress.com/}

%March for science, orga team: \url{http://marchforscienceberlin.de/wer-wir-sind}

%Scientific achievements: \url{http://orcid.org/0000-0002-3127-5520}

\vspace {0.5cm} 

Referees:

Prof. Bjoern Brembs, bjoern@brembs.net
