\section* {Motivation letter}

I hereby apply for the two positions "Beschaeftigter mit abgeschl. wiss. Hochschulbildung" (UB-217/17).% Since I obtained a PhD in 2006, the position would need to be upgraded to a E13 TVoD/Bund.

I used to work in fundamental research (neuro-genetics). In 2013, the boss of my lab moved to south Germany and let me in charge of the ongoing project, which involved one PhD student and one TA. At the end of the project in 2014, I left the academic race and worked on different projects at the HU, (projects involving an interaction with students and engineers, as well as a practical course organisation).  Since then, I gathered more experience in scientific project management, data management and science communication. I am involved in the open science movement and would love to see the linked skills taught to early career researchers. In particular, I think data management should be taught early, not only because it increases the reliability of the research, but also because the scientist will then save an enormous amount of time.


I am looking forward to hear from you,

Dr. Julien Colomb

\vspace {1cm} 

Links:

My website on teaching open science: \\ \url{https://reproducibleresearch.wordpress.com/}

The open science meetup I am running:\\ \url{http://www.meetup.com/Berlin-Open-Science-Meetup/}

%March for science, orga team: \url{http://marchforscienceberlin.de/wer-wir-sind}

%Scientific achievements: \url{http://orcid.org/0000-0002-3127-5520}

\vspace {0.5cm} 

Referees:

Prof. Bjoern Brembs, bjoern@brembs.net
