\section* {Motivation letter}

I hereby apply for the Senior PostDoc Metaresearch position at the BIH.

\vspace {0.5cm} 
  % \emph{A crapy (software) tool that is used is better than a perfect one without user.}

Dear Prof. Dr. Dirnagl,

Metaresearch is a young field and so far, statisticians have been taking the lead. I believe that with my background as a professional researcher in Biology (and my absence of medical training) as well as my interest in scientific report quality, I can bring a different approach to the field and new perspectives to the BIH. 

As you know, I have a strong background in fundamental research in neuro-genetics and behavioural biology. I have been designing experiments for years, with particular interest on control group design, doing experiment blind, in parallel and in a randomised order. I have been trained to find experimental design errors before the start of the experiment, and spot them while looking only at the raw data (obtained from students or other postdocs).

 I also have the computing knowledge to perform quantitative analysis and text mining, although I used these skills in different contexts so far (reproducible data analysis, please have a look at my latest manuscript where I produced R shiny application to archive and analyse mice home cage monitoring data [1]). I am convinced that qualitative meta-analysis (reading the papers) is needed to get a real impression of what data is worth including in the meta-analysis, and I have the skills and knowledge to perform such analyses.
 
I have recently published one paper as a last author and one paper without PI, demonstrating my independent thinking and ability to supervise students. 
I would be happy to continue my journey in science, open science and quality insurance, and work in an environment that will bring more professionalisms and rigour in preclinical research. I am convinced that the field needs more inputs from senior biologists and I would be happy to have the opportunity to prove my point.


Julien Colomb, PhD in Biology



%\vspace {.5 cm} 


%\newpage



%\rubrique {references}


%
Referees:
\begin{itemize}[noitemsep,topsep=0pt]
\item Prof. York Winter, Berlin, york.winter@charite.de
 
\item Prof. Bjoern Brembs, Regensburg, bjoern@brembs.net
\end{itemize}

References
\begin{itemize}[noitemsep,topsep=0pt]

\item [1] \url{https://www.overleaf.com/read/hxwpffyxfbzm}



\end{itemize}
\newpage 

