\section* {Motivation letter}

I hereby apply for the position wissenschaftliche/r Mitarbeiter/in beim Kompetenznetzwerk Forschungsdatenmanagement der Th\"{u}ringer Hochschulen (119/2018)

\vspace {0.5cm} 
  % \emph{A crapy (software) tool that is used is better than a perfect one without user.}

Dear Prof. Dr. Birgitta K\"{o}nig-Ries, dear M. Gerlach,

As a recently got interviewed for a different position in your group and as, at the time of your decision for this position, I will be working in your group, I will only briefly outline my fit to this new position.

My background is neuro-genetics and I have been passionate about open FAIR data and reproducible research since 2012. The development of new tools and strategies enabling better research data management is blooming, but there was so far too little coordination between the universities in their projects. I am glad to see this changing. 
%
In the field of open science education for instance, we see the emergence of new initiatives, both community driven (\url{www.opensciencemooc.eu}) and institution driven (FOSTER Plus project), which will complement personal initiatives like mine (\url{http://rpubs.com/j_colomb/workshops}).

During my interview for the position 98/2018, M. Gerlach could experience my abilities to speak German. I have been organising my time between several projects through the years, working with different teams (constituted from scientists, designers, coders and experts in science communication). I also had the opportunity to give expert advice in experimental design during my work at the AOCF.

Working on the development of Drososhare (a company I founded in 2012), I gathered experience in marketing, online marketing, customer relationship management, legal problematic, and service oriented behaviour.


I hope to be able to show that I can be an real asset for this project, during my work on the development of promotion material for open science in the coming weeks and I am  looking forward to meet you in person.


Dr. Julien Colomb
\\
Schillerpromenade 4
\\
12049 Berlin


%\vspace {.5 cm} 


\newpage



%\rubrique {references}


%
%Referees:
%\begin{itemize}[noitemsep,topsep=0pt]
%\item Prof. York Winter, Berlin, york.winter@charite.de
% 
%\item Prof. Bjoern Brembs, Regensburg, bjoern@brembs.net
%\end{itemize}


\newpage 

