\section* {Motivation letter}

I hereby apply for the Senior Scientist in Natural Sciences or Informat-ics/Computer Science for Statistical Data Analysis (Data Science). (37/18-1.8)

\vspace {0.5cm} 
  % \emph{A crapy (software) tool that is used is better than a perfect one without user.}

Dear Dr. habil. Rudolf J. Schneider,

Although I have no practical experience in HRMS, I have a strong background in data management and analysis. I have recently build R-shiny application to deal with home cage monitoring data in about 3 months, with little knownledge of the data structure beforehand. This work will soon be published, and you can see a draft of the paper online [1].

I have the knowledge and skills necessary for proper data management and analysis and I have developed R, Rmarkdown and RShiny tools during the last years.
As a behavioral biology researcher, I have been trained to find experimental design errors before the start of the experiment, and spot them while looking only at the raw data (obtained from students or other postdocs).

 
I have recently published one paper as a last author and one paper without PI, demonstrating my independent thinking and ability to supervise students. 
I would be happy to use these skills in a new environment at the BAM.


Julien Colomb, PhD in Biology



%\vspace {.5 cm} 


%\newpage



%\rubrique {references}


%
Referees:
\begin{itemize}[noitemsep,topsep=0pt]
\item Prof. York Winter, Berlin, york.winter@charite.de
 
\item Prof. Bjoern Brembs, Regensburg, bjoern@brembs.net
\end{itemize}

References
\begin{itemize}[noitemsep,topsep=0pt]

\item [1] \url{https://www.overleaf.com/read/hxwpffyxfbzm}



\end{itemize}
\newpage 

