
\section* {Application for the job: \\Scientist (systems biology) \& business developer}

\vspace{1cm}

Since my profile on linkedin is far from complete, I would encourage you to read this letter. Indeed, I may be the perfect candidate for your position: I have 10 years experience in fundamental biology, good knowledge in computer science and last but not least, I have written my own business plan while building my startup. With the development of open science, open data and OA publishing, the academic life sciences business model is in mutation. Your company seem to be able to play a significant role in these changes.

I am a neurogeneticist and I started to use R for my statistical analysis about seven years ago. More recently, I used R to analyze more complex data: trajectory of walking animals; a work that was published iin 2012 (\url{http://www.plosone.org/article/info%3Adoi%2F10.1371%2Fjournal.pone.0042247}).
More recently, I worked on the automatic publishing of data in R: On figshare, you can access the learning data I uploaded directly during the data analysis (pre-analysed data here : \url{http://dx.doi.org/10.6084/m9.figshare.830423}). I am thus able to work with R to analyse complex data types. I am also quite good with statistical analysis, although I did not work with omics data so far.

For the last two years, I have been planning and building Drososhare GmbH, a company which aims at facilitating exchange of material between scientists, in particular the sharing of transgenic Drosophila flies. My business plan made it to the 15th place (over 62) in the BPW last year, although it had been written in less than one month. I am participating in the contest again this year (I modified the market size, and therefore the whole plan) and have been following the different workshops proposed by the BPW and the Science4Life contests. I have therefore some experience in business planning, market analysis and marketing strategies.

I am between jobs, since my grant application was refused last november. I am looking for a job in different sectors: academic science as a post doc, a job in the industry as well as Drososhare CEO: I am trying to find investors for my company to finance its development. I would be very interested in talking to your team about your business. As I explained during my panton fellowship application (\url{http://vimeo.com/72518561}), there is a need for private-company solutions dealing with the problems of data analysis and data storage (once scientists are united on the metadata format they want to have). 

If I would not perfectly fit this position, it might be fruitful to discuss the development of a new branch in your business model, where my qualifications would be best used ?


\vspace{1cm}
Sincerely yours,
\\

\hspace{0.6\textwidth} Dr. Julien Colomb


