\section* {Motivation letter}

I hereby apply for the position wissenschaftliche/r Mitarbeiter/in beim Kompetenznetzwerk Forschungsdatenmanagement der Th\"{u}ringer Hochschulen (26/2018) in Erfurt

\vspace {0.5cm} 
  % \emph{A crapy (software) tool that is used is better than a perfect one without user.}

Dear M.  Kuhles,

My background is neuro-genetics and I have been passionate about open FAIR data and reproducible research since 2012. The development of new tools and strategies enabling better research data management is blooming, but there was so far too little coordination between the universities in their projects. I am glad to see this changing. 
%
In the field of open science education for instance, we see the emergence of new initiatives, both community driven (\url{www.opensciencemooc.eu}) and institution driven (FOSTER Plus project), which will complement personal initiatives like mine (\url{http://rpubs.com/j_colomb/workshops}).

I have recently been interviewed for a position at dariah, where M. Romary was very confident in my ability to work with social science data, as the data management does not differ that much between different research fields. In monthly meetups I am co-organising in Berlin, I had the chance to learn from different advocate for open science coming from the humanities.

Working on the development of Drososhare (a company I founded in 2012), I gathered experience in the development of a web presence and service oriented behavior.

I have very recently (15.5.2018) started to work with Prof. Dr. Birgitta K\"{o}nig-Ries and M. Gerlach in Jena on the development of promotion material for open science, as a replacement for a maternity leave. They encouraged me to apply to this position.


Dr. Julien Colomb
\\
Schillerpromenade 4
\\
12049 Berlin


%\vspace {.5 cm} 


\newpage



%\rubrique {references}


%
%Referees:
%\begin{itemize}[noitemsep,topsep=0pt]
%\item Prof. York Winter, Berlin, york.winter@charite.de
% 
%\item Prof. Bjoern Brembs, Regensburg, bjoern@brembs.net
%\end{itemize}


\newpage 

