\section* {Motivation letter}

I hereby apply for the position of Data Manager at PRA.

What I can bring to PRA as an scientific data specialist.

- The successful candidate will have both a commercial and clinical focus, with a real commitment to client satisfaction. A life science or mathematics degree (minimum Bachelor level) is preferred

I got a PhD in neurobiology and have been developing data analysis software for the last years. I created my own startup dealing with a  database for scientists in 2013 (drososhare gmbh).

- Relevant industry/CRO and/or Oracle Clinical experience would be beneficial but is not required

I do not have this experience, but I am learning fast.

- You also have a very good command of German and English

I am fluent in German and English, while my mother tongue is French.

- As needed for early phase patient trials, you are creative and eager to solve also non-standard requirements

Thanks to my large experience and open mind, my creativity is not to be doubted.

I hoped I will be able to convince you of my fit for this position during an interview. Best regards,

\vspace {0.5cm} 
  % \emph{A crapy (software) tool that is used is better than a perfect one without user.}


Julien Colomb, PhD in Biology



%\vspace {.5 cm} 


%\newpage



%\rubrique {references}


%
Referees:
\begin{itemize}[noitemsep,topsep=0pt]
\item Prof. York Winter, Berlin, york.winter@charite.de
 
\item Prof. Bjoern Brembs, Regensburg, bjoern@brembs.net
\end{itemize}





\end{itemize}
\newpage 

