
\subsection*{Peer review publications}

%\rubrique{Peer review publications}
%5 1st author research paper,
%2 review (from which 1 book chapter),
%1 extra-view article\\
%"`publish or perish"` statistics
%Papers:	6	Cites/paper:	3.67	h-index:	3	


 
\subsubsection{Five most important publications:}
\label{sec:FiveMostImportantPublications}

 
\begin{sloppypar}
\newcommand{\enquote}[1]{``#1''}
\providecommand{\bibinfo}[2]{#2}
%
%In prep.
%
%\begin{itemize}
%
%   
%   
%\item  (\bibinfo{year}{-}).
%  \bibinfo{author}{\textbf{Ezequiel~Mendoza}}, \bibinfo{author}{\textbf{Julien~Colomb}}, \bibinfo{author}{Juergen~Rypbak},
%  \bibinfo{author}{Hans-Joachim~Pflueger}, \bibinfo{author}{Troy~Zars}, \bibinfo{author}{Constance~Scharff} and \bibinfo{author}{Björn~Brembs}. \\
%\newblock \enquote{\bibinfo{title}{\textit{Drosophila} FoxP is necessary for operant self-learning.}}
%\newblock \bibinfo{journal}{-}
%  (\bibinfo{pages}{-}).
%   %\\ cited 1 times%google +1
%     
% \end{itemize}
 %
\begin{itemize}   
 
\item  (\bibinfo{year}{2012}).
  \bibinfo{author}{\textbf{Julien~Colomb}}, \bibinfo{author}{Lutz~Reiter},
  \bibinfo{author}{Jedrzej~Blaszkiewicz}, 
  \bibinfo{author}{Jan~Wessnitzer} and \bibinfo{author}{Björn~Brembs}. \\
\newblock \enquote{\bibinfo{title}{Open Source Tracking and Analysis of Adult \textit{Drosophila} Locomotion in Buridan's Paradigm with and without Visual Targets.}}.
\newblock \bibinfo{journal}{Plos One}
  (\bibinfo{pages}{7(8): e42247}).

\item   (\bibinfo{year}{2009}).  
 \bibinfo{author}{\textbf{Julien~Colomb}}, \bibinfo{author}{Laure~Kaiser}, \bibinfo{author}{Marie-Ange~Chabaud}, \bibinfo{author}{Thomas~Preat}.
\\
\newblock \enquote{\bibinfo{title}{Parametric and genetic analysis of Drosophila appetitive long-term memory and sugar motivation}}
\newblock \bibinfo{journal}{Genes Brain and Behaviour}
  (\bibinfo{pages}{8 (4): 407-415}).
   \\cited 22 times%, from which 0 reviews and 1 self
   

   

 
 
  \item  (\bibinfo{year}{2007}).
\bibinfo{author}{\textbf{Julien~Colomb}}, \bibinfo{author}{Nicola~Grillenzoni}, \bibinfo{author}{Ariane~Ramaekers}, and
  \bibinfo{author}{Reinhard F.~Stocker}.\\
\newblock \enquote{\bibinfo{title}{Architecture of the primary taste center of \textit{Drosophila melanogaster} larvae}}.
\newblock \bibinfo{journal}{J. comp. neurol.}
  (\bibinfo{pages}{502: 834-847}).
   \\  cited 35 times%, from which 2 reviews and 7 self
 %\google scholar + 2 self reviews

    \item  (\bibinfo{year}{2007}).
 \bibinfo{author}{\textbf{Julien~Colomb}*}, \bibinfo{author}{R\"{u}diger Bader*}, \bibinfo{author}{Bettina Pankratz},
\bibinfo{author}{Anne Schr\"{o}ck}, \bibinfo{author}{Reinhard F. Stocker}, and \bibinfo{author}{Michael J. Pankratz}.
\\
\newblock \enquote{\bibinfo{title}{Genetic dissection of a neural circuit underlying feeding behavior
in \textit{Drosophila}: distinct morphology of single \textit{hugin} expressing
neurons}}.
\newblock \bibinfo{journal}{J. comp. neurol.}
  (\bibinfo{pages}{502: 848-856}).\\
 * {\footnotesize the two authors participated equally to this work.}
 \\ cited 33 times%, from which at least 4 reviews and 8 self
%\google scholar
\item  (\bibinfo{year}{2007}).
  \bibinfo{author}{\textbf{Julien~Colomb}}, \bibinfo{author}{Nicola~Grillenzoni},
  \bibinfo{author}{Reinhard F.~Stocker}, and \bibinfo{author}{Ariane~Ramaekers}. \\
\newblock \enquote{\bibinfo{title}{Complex behavioural changes after odour exposure in \textit{Drosophila} larva}}.
\newblock \bibinfo{journal}{Anim. Behav.}
  (\bibinfo{pages}{73 (4): 579-85}).
   \\ cited 8 times%, from which 3 reviews and 2 self
   %\google scholar -1 double +1 self review
 \end{itemize}








\end{sloppypar}

\subsubsection{Other Publications }
\label{sec:OtherPublications}

\begin{sloppypar}
\newcommand{\enquote}[1]{``#1''}
\providecommand{\bibinfo}[2]{#2}









%Reviews and comment article
\begin{itemize}
\item   (\bibinfo{year}{2010}).  
 \bibinfo{author}{\textbf{Julien~Colomb}}, \bibinfo{author}{Björn~Brembs} \\
\newblock \enquote{\bibinfo{title}{biology of psychology: "simple conditioning"}}
\newblock \bibinfo{journal}{Communicative and Integrative Biology}
  (\bibinfo{pages}{3 (2): 142-145}).
   \\cited 5 times%, from which 0 reviews and 1 self
   
   
 \item   (\bibinfo{year}{2008}).  
 \bibinfo{author}{\textbf{Julien~Colomb}}\\
\newblock \enquote{\bibinfo{title}{Discriminative learning, learning generalization and masking tests as three strategies to assess olfactory discrimination.}}
\newblock \bibinfo{book}{Animal Behaviour: New Research}
\bibinfo{pages}{185-192}
\\ cited 0 times%, from which 0 reviews and 0 self


 \item   (\bibinfo{year}{2007}).  
 \bibinfo{author}{\textbf{Julien~Colomb}}, \bibinfo{author}{Reinhard F.~Stocker}\\
\newblock \enquote{\bibinfo{title}{Combined rather than separate pathway for hedonic and sensory aspects of taste in  \textit{Drosophila} larvae.}}
\newblock \bibinfo{journal}{FLY}
  (\bibinfo{pages}{1 (4): 232-234}).
 \\
 cited 2 times%, from which 1 reviews and 0 self

\end{itemize}
\end{sloppypar}


